Permits, permit holders, vessels 2

### 2016-06-29 portfolio/text/supp.tex
Edit log difference model notes

where ${ B }_{ 0,j }$ is a normally distributed random effect intercept in the mean (j subscripting different strategies). The interpretation of ${B}_{ 0,j}$ is that each after log-differencing, each strategy has different effects on changes in revenue (some tend to be winners, others tend to be losers). Initial versions of this model included estimating ${ B }_{ 0,j }$, which were largely centered on 0 (as expected), so these random effects were set to 0.  
\newline

The covariate ${ s }_{ t,i }$ is input as data, and represents the percent change in species diversity over the same time period that the percent change in revenue is being modeled, $log\left( \frac { { div }_{ t+1,i } }{ { div }_{ t,i } }  \right)$ where ${ div }_{ t,i }$ is the effective diversity of individual *i* at time *t*. The coefficient ${ B }_{ 1,j }$ is a random effect on the slope, by strategy, representing how much an X% change in species diversity within a strategy translates to a Y% change in revenue.

@@

To account for variable effort over time (changes in revenue could be attributed to diversification, but also to more fishing) we included an offset term ${o}_{t,i}$, representing the percent change in landing dates between years. We experminted with different versions of the offset and when included in the model as a predictor, the coefficient is estimated to be ~ 1, so this is a reasonable assumption. The offset is calculated as $log\left( \frac { { day }_{ t+1,i } }{ { day }_{ t,i } }  \right)$. 
\newline

@@

Finally, the residual error term is also modeled as a linear function of covariates,

${ \sigma  }_{ t,i }=\sqrt { \left( \gamma _{ 0,j }+{ \gamma  }_{ 1,j }\cdot { s }_{ t,i } \right)  }$

where the $gamma _{ 0,j }$ and $gamma _{ 1,j }$ represent random intercepts and slopes in the strategies. I had been interpreting the intercepts as the between-group variability in strategies (some strategies will have more variable % change in revenue than others, similar to some stocks having higher variability in returns). I was interpreting the random slope $gamma _{ 1,j }$ as the effect of within - strategy diversification; in other words, the effect of increases in species diversification varied among different strategies.

>>>>

\noindent
where ${ B }_{ 0,j }$ is a normally distributed random effect intercept in the
mean (j subscripting different strategies). The interpretation of ${B}_{ 0,j}$
is that each after log-differencing, each strategy has different effects on
changes in revenue (some tend to be winners, others tend to be losers). Initial
versions of this model included estimating ${ B }_{ 0,j }$, which were largely
centered on 0 (as expected), so these random effects were set to 0.  \newline

The covariate ${ s }_{ t,i }$ is input as data, and represents the percent
change in species diversity over the same time period that the percent change
in revenue is being modeled, $\log\left( \frac { { div }_{ t+1,i } }{ { div }_{
t,i } }  \right)$ where ${ div }_{ t,i }$ is the effective diversity of
individual $i$ at time $t$. The coefficient ${ B }_{ 1,j }$ is a random effect
on the slope, by strategy, representing how much an X\% change in species
diversity within a strategy translates to a Y\% change in revenue.

@@

To account for variable effort over time (changes in revenue could be
attributed to diversification, but also to more fishing) we included an offset
term ${o}_{t,i}$, representing the percent change in landing dates between
years. We experimented with different versions of the offset and when included
in the model as a predictor, the coefficient is estimated to be ~ 1, so this is
a reasonable assumption. The offset is calculated as $\log\left( \frac { { day
}_{ t+1,i } }{ { day }_{ t,i } }  \right)$. \newline

@@

Finally, the scale of the residual error term is also modeled as a linear
function of covariates,

\begin{equation}
{ \sigma  }_{ t,i }=
\sqrt { \exp \left( \gamma _{ 0,j }+
{ \gamma  }_{ 1,j }\cdot { s }_{ t,i } \right)  }
\end{equation}

\noindent
where the $\gamma_{ 0,j }$ and $\gamma_{ 1,j }$ represent random intercepts and
slopes in the strategies. I had been interpreting the intercepts as the
between-group variability in strategies (some strategies will have more
variable \% change in revenue than others, similar to some stocks having higher
variability in returns). I was interpreting the random slope $\gamma_{ 1,j }$
as the effect of within-strategy diversification; in other words, the effect
of increases in species diversification varied among different strategies.
